% !TEX TS-program = xelatex
% Editor Used = texworks 
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8
% Revision History = v 3.2
% See CV note for Various Changes 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MY PRO RESUME
%% <https://github.com/lttesp/resume>
%% This is free and unencumbered software released into the
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,MMMyyyy,nonstop]{simpleresumecv}
% Class options:
% a4paper, letterpaper, draft, nonstop
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Prabhakaran M.}
\newcommand{\CVTitle}{Prabhakaran M}
\newcommand{\CVWebpage}{https://lttesp.github.io}
%\newcommand{\CVNote}{CV compiled on {\today} }


% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\CVAuthor}

\begin{subtitle}
\href{https://www.google.co.in/maps/place/B1+Town+Police+Station/@12.1289065,78.1592938,19z/data=!4m2!3m1!1s0x3bac16fdb579ea7b:0xece4708cacc17e9a}
{No.2, M Block, Police Quarters, Near B1 Police Station, Dharmapuri - 636701}
\par
\href{mailto:cgprabhakaran@gmail.com}
{cgprabhakaran@gmail.com}
\,\SubBulletSymbol\,
+91\,(979)\,168-6772
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\CVWebpage}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%
%% CAREER OBJECTIVE %%
%%%%%%%%%%%%%%%

\section
{Career Objective}
{Career Objective}
{PDF:CareerObjective}

\emph{To obtain a challenging role so that I can use my capabilities through sincere dedication and hard work to move up the graph of the Organization.}


%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

\href{http://www.kct.ac.in}
{\textbf{Kumaraguru College of Technology}},
Saravanampatty, Coimbatore.

\GapNoBreak
\BulletItem
\emph {Master of Engineering (M.E) in}
\href{http://kct.ac.in/cse.html}
{{Computer Science and Engineering}}
\hfill
\DatestampYMD{2016}{08}{29} --
\DatestampYMD{2018}{05}{01}
\begin{detail}
\SubBulletItem 
Currently Pursuing
\SubBulletItem 
Affliation : Anna University, Chennai.
\SubBulletItem
Semester GPA: 3.60 (Upto 1\textsuperscript{st} Semester)
\end{detail}
\BigGap

\href{http://www.velammal.edu.in}
{\textbf{Velammal Engineering College}},
Surapet, Chennai.

\GapNoBreak
\BulletItem
\emph {Bachelor of Technology (B.Tech) in}
\href{velammal.edu.in/ITnew_aboutdep.html}
{{Information Technology}}
\hfill
\DatestampYMD{2011}{08}{14} --
\DatestampYMD{2015}{05}{08}
\begin{detail}
\SubBulletItem 
Affliation : Anna University, Chennai.
\SubBulletItem
Cumulative GPA: 6.69 / 10
\end{detail}

\BigGap
\href{https://www.google.co.in/#q=sri+vidya+mandir+uthangarai}
{\textbf{Sri Vidya Mandir Matric Higher Sec. School}},
Uthangarai, Krishnagiri.

\GapNoBreak
\BulletItem
\emph{Higher Secondary Education - }
\href{http://www.example.com/my-department}
{12\textsuperscript{th} Standard}
\hfill
\DatestampYMD{2010}{06}{01} --
\DatestampYMD{2011}{05}{27}
\begin{detail}
\SubBulletItem
Board : TN - State Board
\SubBulletItem
Percentage Scored : 86\%
\end{detail}

\BigGap
\href{http://www.vijayvidyalaya.com/matric_dhar/}
{\textbf{Sri Vijay Vidyalaya Matric Higher Sec. School}},
Gandhhi Nagar, Dharmapuri.

\GapNoBreak
\BulletItem
\emph {Secondary School Education -}
\href{}
{10\textsuperscript{th} Standard}
\hfill
\DatestampYMD{2008}{05}{31} --
\DatestampYMD{2009}{04}{06}
\begin{detail}
\SubBulletItem
Board : TN - Matriculation Board
\SubBulletItem
Percentage Scored : 86\%
\end{detail}

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section
{Technical Proficiency}
{Technical Proficiency}
{PDF:Technical Proficiency}

\BulletItem
Operating System : Windows 8, Linux Mint 17 Rebecca 

\GapNoBreak
%\newline
\BulletItem
Programming Languages : C, Java, Python, {\LaTeX} 

\GapNoBreak
%\newline
\BulletItem
Web Technologies : HTML 5, CSS 3, PHP, JavaScript 
%
%\GapNoBreak
%\newline
%\BulletItem
%Software Proficieny : Adobe Photoshop, Adobe Illustrator, Muse, Adobe Edge 

\GapNoBreak
\newline
\BulletItem
Other Tools : Git

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\section
{Interests}
{Interests}
{PDF:Interests}

Web Development,
Data Analytics,
Social Media Analysis


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL AFFILIATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Professional Experience\newline
\& Activities}
{Professional Experience \& Activities}
{PDF:ProfessionaExperienceActivities}

\href{http://www.wideva.com}
{\textbf{WidEva Systems Limited}},
Chennai.

\GapNoBreak
\BulletItem
\emph{Intern , Web Developer}
\hfill
\DatestampYMD{2015}{03}{16} -- \DatestampYMD{2015}{08}{01}

\begin{detail}
\SubBulletItem
Developed company website for WidEva Systems.
\SubBulletItem
Co-ordinated with Tech team for developing portal  using Web2py Framework.
\SubBulletItem
Co-ordinated all UI Development Works.
\end{detail}

\BigGap
\href{http://www.azzept.com}
{\textbf{Azzept Technologies Private Limited}},
Chennai.

\newline

\GapNoBreak
\BulletItem
\emph {Freelance Web Developer}
\hfill
\DatestampYMD{2015}{08}{01} -- \DatestampYMD{2015}{11}{05}

\begin{detail}
\SubBulletItem
Developed company website for Azzept Technologies Private Limited.
\SubBulletItem
Front - End Developer for selective projects.
\end{detail}

\BigGap

%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%

\section
{Campus Activities}
{Campus Activities}
{PDF:CampusActivities}

\href{\#}
{\textbf{Active Co-ordinator - Web Developement Events}},
Velammal Engineering College

\GapNoBreak
\BulletItem
\emph{ Co-ordinator}
\hfill
\DatestampYMD{2014}{08}{14}

\BigGap

\href{\#}
{\textbf{Web Developer \& Designer}},
Department of IT, Velammal Engineering College

\BulletItem
\emph{Web Developer for Department Symposium, Conference and  for all Other Activities }
\hfill
\DatestampYMD{2014}{10}{14}


\BigGap
\href{\#}
{\textbf{Vounteer \& Web Developer}},
E-Cell, Lemon Ivy, Velammal Engineering College

\GapNoBreak
\BulletItem
\emph{Volunteer \& Web Developer } 
\hfill
\DatestampYMD{2013}{03}{14}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Projects}
{Projects}
{PDF:Projects}

{\textbf{Academic Projects}}

\GapNoBreak
\BulletItem
Reliable Load Balancing Routing Protocol in SDN-based \newline Ad-hoc Networks During DDOS Attack.
\hfill
\DatestampYMD{2015}{01}{20} --
\DatestampYMD{2015}{04}{18}
\begin{detail}
\SubBulletItem
Load balancing is a problem of resource distribution which guarantees that all resources are used with maximum utilization. 
In this project, we plan to design a reliable multipath routing protocol which takes both these factors into consideration and also to indentify DOS Attack. 
It is expected to produce better performance against fault or attacks and heavy traffic scenarios.
\end{detail}

\newline

\GapNoBreak
\BulletItem
College Management System Using LAMP Stack
\hfill
\DatestampYMD{2014}{08}{20} --
\DatestampYMD{2014}{11}{23}
\begin{detail}
\SubBulletItem
Since Our College doesn't have any proper management system, I and a group of students gathered requirements from faculties and created a management system using PHP and MySQL(LAMP Stack). Some Special features includes sophisticated Control Panel, Data Visualization using D3.js and so on. 
\end{detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Other Projects}
{Other Projects}
{PDF:OtherProjects}

{\textbf{Freelance Projects}}

\GapNoBreak
\BulletItem
Ticket Management System - Recruiting Services and HR Operations
\begin{detail}
\SubBulletItem
Web App for HR and group of recruiters to keep track of HR Operations and Recruiting Services in a Consultant and Human Resource Company.
Built using Python with Web2py Framework.
\end{detail}

%%%%%%%%%%%%%%%%
%% CERTIFICATIONS %%
%%%%%%%%%%%%%%%%

\section
{Certifications}
{Certifications}
{PDF:Certifications}


\BulletItem
\textbf{Cambridge ESOL Entry Level Certificate in ESOL International }
\newline
\emph {Passed Business English Certificate Preliminary}

\newline
\GapNoBreak
\BulletItem
\textbf{1Z0-803 \& 1Z0-804 Oracle Certified Professional, Java SE 7 Programmer }
\newline
\emph {In Progress, Exam scheduled for April 6, 2016}


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% EXTRA CURRICULAR ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Co-Curricular Activities}
{Co-Curricular Activities}
{PDF:CoCurricularActivities}

%{\textbf{Freelance Projects}}

\GapNoBreak
\BulletItem
Participated in Hackerrank with handle @\href{http://hackerrank.com/lttesp} \emph{lttesp}

\GapNoBreak
\BulletItem
Contributed Open Source projects in Github with handle @\href{http://hackerrank.com/lttesp} \emph{lttesp}

%%%%%%%%%%%%%%% 
%% KEY STRENGTHS %%
%%%%%%%%%%%%%%%

\section
{Key Strengths}
{Key Strengths}
{PDF:KeyStrengths}

\BulletItem
Fast Learner

\GapNoBreak
\BulletItem
Problem Solving

\GapNoBreak
\BulletItem
Team worker

\GapNoBreak
\BulletItem
Adaptable

\GapNoBreak
\BulletItem
Flexibility

%%%%%%%%%%%%%%% 
%% HOBBIES %%
%%%%%%%%%%%%%%%

\section
{Hobbies}
{Hobbies}
{PDF:Hobbies}

\BulletItem
Surfing

%
%\GapNoBreak
%\BulletItem
%Reading Books

\GapNoBreak
\BulletItem
Blogging

\GapNoBreak
\BulletItem
Creative Designing 

%%%%%%%%%%%%%%
%% WEB PRESENCE %%%%%
%%%%%%%%%%%%%%%

\section
{Web Presence}
{Web Presence}
{PDF:WebPresence}

\BulletItem
Quora (I write and read) : https://www.quora.com/Prabhakaran-Sp-2
\GapNoBreak

\BulletItem
GitHub (I share my code) : https://github.com/lttesp

\GapNoBreak
\BulletItem
Blog (I share my experiences) : https://lttesp.github.io/blog

%%%%%%%%%%%%%%% 
%% LANGUAGES %%%%%%%
%%%%%%%%%%%%%%%

\section
{Languages}
{Languages}
{PDF:Languages}

\BulletItem
Tamil : Mother Tongue (Speaking, Reading , Writing).

\GapNoBreak
\BulletItem
English : Native language (Speaking, Reading , Writing).

%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

\section
{References}
{References}
{PDF:References}

\BulletItem
\textbf{Mr. Dinesh Gunasekar}
\newline
Founder \& CTO, WidEva Systems Private Limited
\newline
\href{mailto:danny@osdefsec.com}
{danny@osdefsec.com}

\BulletItem
\textbf{Mr. Parthiban K.}
\newline
HR Manager, Azzept Technologies Private Limited
\newline
\href{mailto:parthiban@ruinfotech.com}
{parthiban@ruinfotech.com}

\end{body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

%\UseNoteFont%
%\null\hfill%
%[\textit{\CVNote}]%
%\hspace{2.0mm}\null

\end{document}
